---
title: "Ruam P. F. A. Pimentel's CV"
author: Ruam P. F. A. Pimentel
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results = 'asis', 
  echo = FALSE
)
library(readr)
library(magrittr)
library(stringr)
source("cv_printing_functions.r")
source("helper_functions.R")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "data/",  
  pdf_mode = params$pdf_mode
)

zotero <- read_csv("data/zotero_pimentel_2023-02-22.csv") %>% 
  janitor::clean_names()
# zotero %>% glimpse()

zotero_cleaned <- zotero %>%
  select(item_type:publication_title, doi, url, date, pages, num_pages, issue, volume,
         conference_name, place, type, meeting_name, publisher) %>% 
  # remove preregistration, because it is showing as journal article
  filter(!str_detect(author, "Open Science")) %>% 
  
  mutate(count_authors = str_count(author, ";") + 1,
         author = str_replace_all(author,
                                  "\\b([A-Za-zçé])[A-Za-zçé]* ",
                                  "\\1. ") %>% 
           str_replace_all("\\b([A-Za-zçé])[A-Za-zçé]*;",
                           "\\1. ;") %>% 
           str_replace_all("\\b([A-Za-zçé])[A-Za-zçé]*$",
                           "\\1.") %>% 
           str_replace_all("\\b([a-zçé])[a-zçé]*.","") %>% 
           str_replace_all(". ;", ".;"),
         author = str_replace(author, ";(?!.*;)", " &"))


  
```

```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```

# Aside

<!-- Swap image with your preferred logo -->

<!--![logo](https://cran.r-project.org/Rlogo.svg){width=100%} -->

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
# datadrivencv::build_network_logo(CV$entries_data)
```

```{r}
if(params$pdf_mode){
  cat("View this CV online with links at [ruampimentel.github.io/Pimentel_CV/cv.html](https://ruampimentel.github.io/Pimentel_CV/cv.html)")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/ruampimentel/Pimentel_CV/blob/main/cv.pdf)")
}
```

## Contact {#contact}

```{r}
CV %>% print_contact_info()
```

## Relevant skills {#skills}
### Data Analysis
- Statistics, Psychometrics
- Data Visualization
- Structural Equation Modeling
- Machine Learning Models

### Tech
- R, Rstudio
- git, GitHub, SQL
- MPlus, SPSS
- Some Python

## Language {#language}

```{r rskills, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(CV$skills, "language")

```

## Disclaimer {#disclaimer}

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown).
The source code is available [on github.com/ruampimentel/ Pimentel_CV](https://github.com/ruampimentel/Pimentel_CV).
Last updated on `r Sys.Date()`.



# Main

## Ruam P. F. A. Pimentel {#title}

```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```

## Education {data-icon="graduation-cap" data-concise="true"}

```{r}
CV %<>% print_section('education')
```

\newpage 

## Relevant Courses and Workshops {data-icon="laptop"}

```{r}

CV %<>% print_section('relevant_courses')
```

\newpage 


## Research Experience {data-icon="laptop"}

```{r}
CV %<>% print_section('research_positions')
```



## Teaching Experience {data-icon="chalkboard-teacher"}

::: aside
```{r}
CV %<>% print_text_block('teaching_experience_aside')
```
:::

```{r}
CV %<>% print_section('teaching_positions')
```


## Peer Reviewed Publications {data-icon="book"}
::: aside
```{r}
CV %<>% print_text_block('publications_aside')
```
:::

```{r}
print_output_section(zotero_cleaned, "journalArticle")
# CV %<>% print_section('journalArticle')
```


## Conference Presentations {data-icon="comments"}


::: aside
```{r}
CV %<>% print_text_block('conference_presentation_aside')
```
:::

```{r}
print_output_section(zotero_cleaned, "presentation")
```

## Conference Papers {data-icon="newspaper-o"}


```{r}
print_output_section(zotero_cleaned, "conferencePaper")
```

\newpage

## Unpublished Work {data-icon="pencil"}

::: aside
```{r}
CV %<>% print_text_block('unpublished_work_aside')
```
:::

```{r}
print_output_section(zotero_cleaned, "thesis")
```



## Miscellaneous - Skills and Hobbies

```{r}
CV %<>% print_section('miscellaneous')
```

